---
title: "Assignment 1"
author: "Dr Thomas Robinson and Dr Dan de Kadt"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE} 
# this chunk contains code that sets global options for the entire .Rmd. 
# we use include=FALSE to suppress it from the top of the document, but it will still appear in the appendix. 

knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options. 
# we set echo=FALSE to suppress code such that it by default does not appear throughout the document. 
# note: this is different from .Rmd default
```

### Exercise 1

Here, I will be answering exercise one. This is a test and I will be presenting the results of a for loop printing the numbers from 1 to 10.

```{r codechunk_name}
# For loop to print the numbers from 1 to 20
for (i in 1:20) {
  print(i)
}

```
This prints the numbers 1 to 20, each on a separate line. This concludes exercise 2.


```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
